Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-22 manuscript/response_to_reviews.Rmd

e. Table 1: (i) The definition of GPP refers to NEE, but this in never defined. The preceding entry defines NEP not NEE. (ii) The description of the biome labels is inaccurate. The table uses "TrB" but the note refers to "Tr". The table uses "BoN", but the note refers to "B".

**We have fixed both of these.**

f. Line 210: I am confused by the statement that of the 39762 records in ForC v3.0, 11923 were included in this study. Previously (lines 135-149), the authors described creating "ForC-simplified" with 17349 records. Clarify the difference between ForC-simplified and ForC v3.0.

**It appears that reference to ForC-simplified (essentially an automatically generated rearrangement of ForC that is purged of duplicates and organized for easy analysis) makes the process more confusing, and isn't necessary, so we eliminated mention of it.**

@@

g. Line 212: The authors refer to ForC, where in the previous sentence they referred to ForC v3.0, and previously used ForC-simplified. Clarify what database is used in the analyses.

**As in the response above, we have eliminated unnecessary/confusing mention of ForC-simplified. The version used is ForC v3.0 (to be released with DOI upon acceptance of this manuscript). We do not feel it is necessary to state the version number every time ForC is mentione.**

@@

a. Yes, there is a need for this database; but

b. No, this is not a critical and authoritative review of the carbon cycle; and

c. The authors reference many other publications and datasets, but they do not critically evaluate their own dataset or other datasets.

**We'd define this as a "quantitative review"--*i.e.*, one that quantitatively synthesizes previous studies. However, we agree that the previous version did little to critically review the corresponding literature. To improve in this area, we have expanded and reorganized the introduction into four sub-sections ("Forests in the global C cycle: current and future", "Evolution of forest C cycle research", "Biome differences", and "Age trends and their variation across biomes"). The latter three sections are mostly or entirely new relative to the previous version, and briefly review the development and current status of the science on each topic. We have also added a schematic figure (Fig. 1) to summarize current understanding of each topic and help with conceptual framing of the review. We also shifted emphasis more towards the ecological questions (trends across biomes and with age), while retaining (with less emphasis) the analysis of database representativeness.**

### 2021-01-22 manuscript/ERL_global_C_review.Rmd
finished responses to R2

To facilitate analyses, we created a simplified version of ForC, *ForC-simplified* (https://github.com/forc-db/ForC/blob/master/ForC_simplified), which we analyzed here.
In generating *ForC-simplified*, all measurements originally expressed in units of dry organic matter ($OM$) were converted to units of C using the IPCC default of $C = 0.47 * OM$ [@ipcc_global_2018].
Duplicate or otherwise conflicting records were reconciled as described in Appendix S1, resulting in a total of `r ForC_simplified_duplicates_removed` records (`r round(ForC_simplified_duplicates_removed/nrow(ForC_measurements)*100,digits=1)`% size of total database).
Records were filtered to remove plots that had undergone significant anthropogenic management or major disturbance since the most recent stand initiation event.
Specifically, we removed all plots flagged as managed in ForC-simplified (`r round(n_managed_in_ForC_simplified/ForC_simplified_duplicates_removed*100,digits=1)`%).
This included plots with any record of managements manipulating CO~2~, temperature, hydrology, nutrients, or biota, as well as any plots whose site or plot name contained the terms “plantation”, "planted", “managed”, “irrigated”, or “fertilized”.
Plots flagged as disturbed in ForC-simplified (`r round(n_disturbed_in_ForC_simplified/ForC_simplified_duplicates_removed*100,digits=1)`%) included stands that had undergone any notable anthropogenic thinning or partial harvest.
We retained sites that were grazed or had undergone low severity natural disturbances (<10% mortality) including droughts, major storms, fires, and floods.
We removed all plots for which no stand history information had been retrieved (`r round(n_no_history/ForC_simplified_duplicates_removed*100,digits=1)`%).
In total, this resulted in `r records_eligible_for_inclusion` records (`r round(records_eligible_for_inclusion/nrow(ForC_measurements)*100,digits=1)`% of the records in the database) being eligible for inclusion in the analysis.

>>>>

All measurements originally expressed in units of dry organic matter ($OM$) were converted to units of C using the IPCC default of $C = 0.47 * OM$ [@ipcc_global_2018].
Duplicate or otherwise conflicting records were purged as described in Appendix S1, resulting in a total of `r ForC_simplified_duplicates_removed` records (`r round(ForC_simplified_duplicates_removed/nrow(ForC_measurements)*100,digits=1)`% size of total database).
Records were filtered to remove plots that had undergone significant anthropogenic management or major disturbance since the most recent stand initiation event.
Specifically, we removed plots with any record of managements manipulating CO~2~, temperature, hydrology, nutrients, or biota, as well as any plots whose site or plot name contained the terms “plantation”, "planted", “managed”, “irrigated”, or “fertilized” (`r round(n_managed_in_ForC_simplified/ForC_simplified_duplicates_removed*100,digits=1)`% of duplicate-purged records).
We also removed stands that had undergone any notable anthropogenic thinning or partial harvest (`r round(n_disturbed_in_ForC_simplified/ForC_simplified_duplicates_removed*100,digits=1)`% of duplicate-purged records).
We retained sites that were grazed or had undergone low severity natural disturbances (<10% mortality) including droughts, major storms, fires, and floods.
We removed all plots for which no stand history information had been retrieved (`r round(n_no_history/ForC_simplified_duplicates_removed*100,digits=1)`%).
In total, this resulted in `r records_eligible_for_inclusion` records (`r round(records_eligible_for_inclusion/nrow(ForC_measurements)*100,digits=1)`% of the records in the database) being eligible for inclusion in the analysis.
